The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-05-19 head.tex
细微调整结构框架，准备开始框架修改和文献综述并行。
start the report
添加了逻辑图，改善文章结构，主要在方法上
add the abstract
add ref item
一些新的想法

\title{Net title
%Cloud Manufacturing Ecosystem - Scheduling And Evolving
}

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
New abstract
% In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were constructed standardly by resources is required, in order for the collaboration within the whole Industry Chain.
%This paper 
%\begin{inparaenum}[1)]
%\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
%\item modeled the services scheduling matter in the chain;
%\item designed evolving modules for the Cloud Manufacturing Ecosystem;
%\item opened some Ecosystem related issues. 
%\end{inparaenum}
%With the help of Data Science tools on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
%gradually evolve the ecosystem to an optimal situation.

>>>>

\title{The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture
%Cloud Manufacturing Ecosystem - Scheduling And Evolving
}

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
New abstract
% 提出了 Cloud Manufacturing Ecosystem 概念，建立相应的生态系统模型，从系统中的各个角色，（需要一个指标）建立系统动力学方程。通过仿真手段验证模型，结合已有的云平台原型系统，给出相关应用。
% 云制造的实施和应用提供了一种全新的制造业生态系统，该生态系统由成员（企业用户、管理员）及环境（）组成。为了探究生态系统中，制造业的运作模式（相关决策），优化产业链，形成良性发展的制造生态，通过基于Agent 的建模，来刻画该系统中的个体行为，并通过仿真技术，模拟演化规律。

% 云制造生态系统中，不同的企业具有不同的生态位
% 该系统的输入
% 输出
% 调控方式

% 通过仿真，我们发现。。。

The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)
% 关键是系统动力学模型的建立。
